Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-05 SAiP/Module1/H1/doc/paper.tex
Updating the sequence diagram with some variable names and fixing type-o in LaTex.

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 600 420,scale=0.5]{figures/cc_ao.pdf}}
\caption{HS07 Active Objects}
\label{fig:cc_ao}
\end{figure}
The sequence diagram illustrates the protocol of the interactions involved in the setup and the execution of the Gateway. It consists of a registration sequence and an infinite loop of retrieving the temperature of all registered themometers and nitifying all observers (in this case the Radiators). The example is slightly simplified to improve readability, as the registerThermometer, registerObserver, getTemperature and notify is actually network calls performed using the Invoker and the respective servers.
\begin{figure}[!htb]
\includegraphics[angle=90,scale=1.2]{figures/sequence.pdf}
\caption{HS07 Sequence Diagram}
\label{fig:sequence}
\end{figure}
\clearpage

@@

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 700 350,scale=0.4]{figures/deployment.pdf}}
\caption{HS07 Allocation Diagram}
\label{fig:allocation}
\end{figure}

% =====================================================================
\section{Discussion}
\subsection{Strength and Limitations of the approach}
%$<<$What are the strengths and limitations of this approach to architectural description judging from this case?$>>$

When using the approach described in \cite{christensen2004archdesc} with reverse 
engineering to achieve an architectural description, the dangers posed seem to 
be finding the correct balance in the choice of detail level. It
is easy to get too much information, cluttering the purpose of the 
AD, which in a basic sense is to clarify and present at wider understanding of
the system.

Experienced architects might recognize patterns emerging from the process, and 
immediately see possible design flaws in the implementation of these, thus
being able to help improve the quality of any evolving system.

The purpose of doing a reverse engineered AD must either be to evolve
the system or to extract clarification. Care should be taken to achieve either
goal. 
\subsection{Whats missing?}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
Stakeholders and their concerns. This encompasses both users/aquirers and developers. We also need to discuss the feasibility and maintainablity of the system.

>>>>

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 600 420,scale=0.5]{figures/cc_ao.pdf}}
\caption{HS07 Active Objects}
\label{fig:cc_ao}
\end{figure}

The sequence diagram illustrates the protocol of the interactions involved in the 
setup and the execution of the Gateway. It consists of a registration sequence and 
an infinite loop of retrieving the temperature of all registered themometers and 
notifying all observers (in this case the Radiators). The example is slightly 
simplified to improve readability, as the registerThermometer, registerObserver, 
getTemperature and notify is actually network calls performed using the Invoker and 
the respective servers.

\clearpage

\begin{figure}[!htb]
\center {\includegraphics[angle=270,scale=0.5]{figures/sequence.pdf}}
\caption{HS07 Sequence Diagram}
\label{fig:sequence}
\end{figure}

@@

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 700 350,scale=0.5]{figures/deployment.pdf}}
\caption{HS07 Allocation Diagram}
\label{fig:allocation}
\end{figure}

% =====================================================================
\section{Discussion}
\subsection{Strength and Limitations of the approach}
%$<<$What are the strengths and limitations of this approach to architectural description judging from this case?$>>$
\subsection{Strengths}
\begin{itemize}
\item UML is a language that is unambigious and known by many.
\item The three viewpoints are tried and proven, and due to this fact many developers are used to thinking in this way and can generate an understanding of the system based on these views.
 \item Having a well-understandable architecture to go by, makes it easier for multiple developers to work in parallel with a common understanding of the priorities inherint in the architecture.
\end{itemize}

\subsection{Limitations}
\begin{itemize}
\item Just like with any other language it only makes sense to those who know the language. 
\item Choosing three views to focus on, due to the fact that they fit most of the time, means that the focus will sometimes be wrong.
\end{itemize}

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{itemize}
\item \emph{Stakeholders and their concerns}. This encompasses both users/aquirers and developers. \item \emph{Ffeasibility}
\item \emph{Maintainablity}
\item \emph{Security} How is the Gateway protected? What protection is there against attack and inproper use? 
\item \emph {Safety} How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item \emph{Availability} What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item \emph{Testability} What is the tesability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{itemize}
